A minimal reaction-diffusion neural model generates {\emph{C. elegans}} undulation

### 2020-12-25 paper.tex
Fix references

    The small (1 mm) nematode \emph{Caenorhabditis elegans} has become widely used as a model organism; in particular the \emph{C. elegans} connectome has been completely mapped, and \emph{C. elegans} locomotion has been widely studied (c.f. http://www.wormbook.org \citet{corsi2015}) *** also other ref ***. We describe a minimal reaction-diffusion model for the \emph{C. elegans}, which results in similar behaviour to the neuromechanical model of \citet{izquierdo2018}. This  may be considered as a simple model for Xu et al.'s "descending pathway" description of the \emph{C. elegans} central pattern generator (CPG) \citet{xu2018,wen2012}. \citet{olivares2019} present a likely more realistic model which relies on small networks of neurons, and presents a distributed model of the CPG. In particular, we use simulation methods to show that a small network of \citet{fitzhugh1955}-\citet{nagumo1962} neurons (one of the simplest neuronal models) can generate key features of \emph{C. elegans} undulation (see \citet{magnes2012}), and thus locomotion.  Finally, we recreate the required oscillations and coupling with a network of coupled \citet{keener1983} analog neurons.
    \citet{olivares2018potential}
    \citet{olivares2019}
    % TODO: expand and inflate; fix grammar, cite Olivares2019, \citet @article{olivares2018potential}

@@

% TODO - acknowledge prior work by Izquierdo et al.  May be more biologically relevant.  The role of this paper is to show a very minimal example.  We slightly modified the original FHN.

Olivares et al *** recently created a more biologically relevant model for the CPG, which argues that the CPG is a network of connected oscillators.  The role of this paper is to show a very minimal model, and our approach has been to create a small and computationally cheap model.

@@

\begin{figure}[h!]
    \label{fig: cpg}
    \centering
    \inputtikz{figures/cpg/cpg}
    \caption{Our simplified central pattern generator model.  Descending coupling (shows inhibitory connections, and potential flows through gap junctions, not necessarily symmetric)}
\end{figure} % TODO: legend

@@

\subsection{}
% TODO: write up a section on the Beer paper and see how it relates to our CPG model.
% Perhaps a discussion about the "scientific lineage" of our model, and the Olivares et al model.
% Paraphrase their description.

>>>>

    The small (1 mm) nematode \emph{Caenorhabditis elegans} has become widely used as a model organism; in particular the \emph{C. elegans} connectome has been completely mapped, and \emph{C. elegans} locomotion has been widely studied (c.f. http://www.wormbook.org \citet{corsi2015}). We describe a minimal reaction-diffusion model for the \emph{C. elegans}, which results in similar behaviour to the neuromechanical model of \citet{izquierdo2018}. This  may be considered as a simple model for Xu et al.'s "descending pathway" description of the \emph{C. elegans} central pattern generator (CPG) \citet{xu2018,wen2012}. \citet{olivares2019} present a likely more realistic model which relies on small networks of neurons, and presents a distributed model of the CPG. In particular, we use simulation methods to show that a small network of \citet{fitzhugh1955}-\citet{nagumo1962} neurons (one of the simplest neuronal models) can generate key features of \emph{C. elegans} undulation (see \citet{magnes2012}), and thus locomotion.  Finally, we recreate the required oscillations and coupling with a network of coupled \citet{keener1983} analog neurons.
    \citet{olivares2019}
    % TODO: expand and inflate; fix grammar, cite Olivares2019, \citet @article{olivares2018potential}

@@

\citet{olivares2019} recently created a more biologically relevant model for the CPG, which argues that the CPG is a network of connected, self-oscillating systems.  The role of this paper is to show a very minimal model, and our approach has been to create a small and computationally cheap model.

@@

\begin{figure}[h!]
    \centering
    \inputtikz{figures/cpg/cpg}
    \label{fig: cpg}
    \caption{Our simplified central pattern generator model.  Descending coupling (shows inhibitory connections, and potential flows through gap junctions, not necessarily symmetric)}
\end{figure} % TODO: legend

@@

\subsection{Relevance of \citet{izquierdo2018} to our model}
% TODO: write up a section on the Beer paper and see how it relates to our CPG model.
% Perhaps a discussion about the "scientific lineage" of our model, and the Olivares et al model.
% Paraphrase their description.

The \citet{izquierdo2018} model is based on physical realities, and was generated using an evolutionary modelling process to find the structure of the descending neural network which controls muscular motion.  As a result, the model, while realistic, is complex, and differs from ours in several places.  First, the model is not a simple descending linked chain but a complex graphlike structure with repeating, complex self-oscillatory systems of neurons.

Our goal in modelling \emph{C. elegans} is not to produce a very physically accurate model, but rather to replicate those behaviours which are essential - and only those - to the movement of the nematode.  As such, we have the liberty of producing a simpler and more easily quantifiable model.
